Gamification Effectiveness on Education

### 2024-04-15 paper/paper.qmd
mention sample size for each group
forget to include this in the last commit lol

The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control, Educational game, Gamification Plugin, Social networking website, Social gamified networking website. The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with hybrid learning. This course is an introduction to basic computing concepts such as word processing, spreadsheets, presentations and databases. There is an assignment for each of these four concepts which focus on testing practical skills. While, the final examination is cumulative and focus on testing conceptual knowledge.

@@

For our replication, we drop 20 rows of data from the original dataset provided since those rows contained missing data on grades of some assessments and final examination. The age row was removed since in the original study it mention that there age range for each group but in the dataset provided they made every value in that column to 19 since that the average age in the study.

>>>>

The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control(N=76), Educational game(N=75), Gamification Plugin(N=77), Social networking website(N=75), Social gamified networking website(N=76). The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with hybrid learning. This course is an introduction to basic computing concepts such as word processing, spreadsheets, presentations and databases. There is an assignment for each of these four concepts which focus on testing practical skills. While, the final examination is cumulative and focus on testing conceptual knowledge.

@@

For our replication, we drop 20 rows of data from the original dataset provided since those rows contained missing data on grades of some assessments and final examination. The age row was removed since in the original study it mention that there age range for each group but in the dataset provided they made every value in that column to 19 since that the average age in the study. To summarize, the size of the dataset we use in this replication is N = 359 (Control=75, Game=66, Plugin=73, Social Network=74, Social Gamification=71)

This dataset was chosen since my many studies in gamification don't have easy access to their datasets and this dataset includes control and treatment group which is useful for examining the difference between a traditonal education system and gamification.

## 2.4 Data Analysis
